\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-21 paper.qmd
Update screen shots and videos of MNIST

According to @fig-mnist1_sc1, the non-linear continuous structure observed in the \gD{} representation of PaCMAP (see @fig-pacmap-author) is also visible when visualizing the model overlaid on the data space. This indicates that PaCMAP accurately captures the structure of the \pD{} data. Additionally, the model shows a twisted pattern within the non-linear structure in \pD{} space (see @fig-mnist1_sc2), which is an additional pattern not visible in the \gD{} representation (see @fig-pacmap-author). Furthermore, as shown in @fig-mnist1_sc3, some long edges exist in the \pD{} space that are not recognized as long edges in the \gD{} representation. However, PaCMAP is a *good* \gD{} representation of MNIST digit 1 data.

@@

::: {#fig-mnist1_sc layout-ncol="3" fig-pos="H"}
![](figures/mnist/sc_1.png)

![](figures/mnist/sc_2.png)

![](figures/mnist/sc_3.png)

Screen shots of the **langevitour** of the MNIST digit 1 data set, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/zq2GM9qvUNA>).
:::
<!-- need to update the youtube recording-->

>>>>

According to @fig-mnist1_sc1, the non-linear continuous structure observed in the \gD{} representation of PaCMAP (see @fig-pacmap-author) is also visible when visualizing the model overlaid on the data space. This indicates that PaCMAP accurately captures the structure of the \pD{} data. Additionally, the model shows a twisted pattern within the non-linear structure in \pD{} space (see @fig-mnist1_sc2), which is an additional pattern not visible in the \gD{} representation (see @fig-pacmap-author). Furthermore, as shown in @fig-mnist1_sc3, some long edges exist in the \pD{} space that are not recognized as long edges in the \gD{} representation. However, PaCMAP is a reasonable \gD{} representation of MNIST digit 1 data. Because PaCMAP preserves the local structure.

@@

::: {#fig-mnist1_sc layout-ncol="3" fig-pos="H"}
![](figures/mnist/sc_1.png){#fig-mnist1_sc1}

![](figures/mnist/sc_2.png){#fig-mnist1_sc2}

![](figures/mnist/sc_3.png){#fig-mnist1_sc3}

Screen shots of the **langevitour** of the MNIST digit 1 data set, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/zcg_GXBmqjA>).
:::
<!-- need to update the youtube recording-->

### 2024-05-21 paper.tex
Update screen shots and videos of MNIST

According to \textbf{?@fig-mnist1\_sc1}, the non-linear continuous
structure observed in the \gD{} representation of PaCMAP (see
Figure~\ref{fig-pacmap-author}) is also visible when visualizing the
model overlaid on the data space. This indicates that PaCMAP accurately
captures the structure of the \pD{} data. Additionally, the model shows
a twisted pattern within the non-linear structure in \pD{} space (see
\textbf{?@fig-mnist1\_sc2}), which is an additional pattern not visible
in the \gD{} representation (see Figure~\ref{fig-pacmap-author}).
Furthermore, as shown in \textbf{?@fig-mnist1\_sc3}, some long edges
exist in the \pD{} space that are not recognized as long edges in the
\gD{} representation. However, PaCMAP is a \emph{good} \gD{}
representation of MNIST digit 1 data.

@@

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/mnist/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/mnist/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/mnist/sc_3.png}\end{minipage}%

\caption{\label{fig-mnist1_sc}Screen shots of the \textbf{langevitour}
of the MNIST digit 1 data set, shows the model-in-data space, a video of
the tour animation is available at
(\url{https://youtu.be/zq2GM9qvUNA}).}

>>>>

According to Figure~\ref{fig-mnist1_sc1}, the non-linear continuous
structure observed in the \gD{} representation of PaCMAP (see
Figure~\ref{fig-pacmap-author}) is also visible when visualizing the
model overlaid on the data space. This indicates that PaCMAP accurately
captures the structure of the \pD{} data. Additionally, the model shows
a twisted pattern within the non-linear structure in \pD{} space (see
Figure~\ref{fig-mnist1_sc2}), which is an additional pattern not visible
in the \gD{} representation (see Figure~\ref{fig-pacmap-author}).
Furthermore, as shown in Figure~\ref{fig-mnist1_sc3}, some long edges
exist in the \pD{} space that are not recognized as long edges in the
\gD{} representation. However, PaCMAP is a reasonable \gD{}
representation of MNIST digit 1 data. Because PaCMAP preserves the local
structure.

@@

\begin{minipage}{0.33\linewidth}

\captionsetup{labelsep=none}\includegraphics{figures/mnist/sc_1.png}

\subcaption{\label{fig-mnist1_sc1}}

\end{minipage}%
%
\begin{minipage}{0.33\linewidth}

\captionsetup{labelsep=none}\includegraphics{figures/mnist/sc_2.png}

\subcaption{\label{fig-mnist1_sc2}}

\end{minipage}%
%
\begin{minipage}{0.33\linewidth}

\captionsetup{labelsep=none}\includegraphics{figures/mnist/sc_3.png}

\subcaption{\label{fig-mnist1_sc3}}

\end{minipage}%

\caption{\label{fig-mnist1_sc}Screen shots of the \textbf{langevitour}
of the MNIST digit 1 data set, shows the model-in-data space, a video of
the tour animation is available at
(\url{https://youtu.be/zcg_GXBmqjA}).}
